Type Visualization for R

### 2020-06-18 paper/main.tex
paper: Finish paragraph on decrossing

% decrossing

>>>>

Flow layout is a critical consideration
for a sufficiently legible visualization.
Figure~\ref{fig:decross} exemplifies what
happens if flow layout is not adequately handled.
The top layout was generated without any
flow decrossing algorithm,
while the bottom layout does
apply decrossing.
Even with highlighting,
the utility of the visualization is vastly
reduced without some decrossing effort.
To maintain real-time performance,
we use two different decrossing methods.
First, the system attempts to construct
a layout with the globally optimal
minimum amount of flow crossing by
solving a mixed-integer linear program.
Unfortunately, for even moderately
sized graphs this can take too long to compute.
Therefore, after about $1$ second
the optimal algorithm is terminated
if it has not finished, and a faster
algorithm that only locally minimizes crossing
between layers computes the layout.
